Future challenges for Research Software Engineering

### 2025-09-24 future_challenges_for_RSEng.tex
feat(#44): fix tense

Looking ahead over a 10-year time frame, we hope that the RSE community will have
contributed to making research software and its outputs
more sustainable, robust and maintainable.
We also hope that research software becomes an accepted research artefact on an equal footing with data publications and traditional text publications.
This is already happening in a number of ways,
particularly through movements such as DORA~\cite{DORA} and CoARA~\cite{COARA} which are advocating for a change in the way that research is assessed and outputs recognised.
However, we want to ensure that one of the core achievements made by the RSE community in this time
frame is putting the infrastructure and training opportunities in place, alongside the necessary
advocacy, to ensure that researchers receive core software skills as part of their scientific training.
Developing software tools and scripted workflows is becoming an increasingly important part of everyday
research activities.
Therefore, it is vital to improve digital skills of all researchers.
This will also allow RSEs to focus on other more advanced and specialist areas.
In this context, we do not foresee the demise of the RSE as an independent role.
However, we do see the work of RSEs developing and shifting as the research community changes~\cite{ChueHong2025}.

>>>>

Looking ahead over a 10-year time frame, we hope that the RSE community will have
contributed to making research software and its outputs
more sustainable, robust and maintainable.
We also hope that research software will have become an accepted research artefact on an equal footing with data publications and traditional text publications.
This is already happening in a number of ways,
particularly through movements such as DORA~\cite{DORA} and CoARA~\cite{COARA} which are advocating for a change in the way that research is assessed and outputs recognised.
However, we want to ensure that one of the core achievements made by the RSE community in this time
frame is putting the infrastructure and training opportunities in place, alongside the necessary
advocacy, to ensure that researchers receive core software skills as part of their scientific training.
Developing software tools and scripted workflows is becoming an increasingly important part of everyday
research activities.
Therefore, it is vital to improve digital skills of all researchers.
This will also allow RSEs to focus on other more advanced and specialist areas.
In this context, we do not foresee the demise of the RSE as an independent role.
However, we do see the work of RSEs developing and shifting as the research community changes~\cite{ChueHong2025}.
